---
title: "Seedset by Era"
author: "Valerie Martin"
date: "1/24/2020"
output: word_document
---

## Analysis of skypilot seedset/plant and seedset/fruit using era as a predictor variable

```{r include=FALSE}
#Importing data
MergedData <- read.csv("Skypilot Selection/Data/MergedData_Seedset.csv")

#Setting up libraries
library(plyr)
library(nlme)
library(car)
library(emmeans)
library(ggplot2)


MergedData$No.SeedsPerFlower <- as.numeric(as.character(MergedData$No.SeedsPerFlower))
MergedData <- MergedData[-c(278),]
```

*It looks like the only roughly normally distributed response variable is total no. of flowers*
```{r echo=FALSE}
qqnorm(MergedData$Total.Flowers)
qqline(MergedData$Total.Flowers)
```


*The other response variables appear to have high 0 counts, and look to be roughly Poisson distributed.*
*That said, Poisson is usually for integer count data - should I use it in the case of Seeds/Fruit and Seeds/Flower?*
*Seeds/fruit looks like it may have a roughly normal distribution if the 0's are taken out.*

```{r echo=FALSE}
qqnorm(MergedData$No.Fruits)
qqline(MergedData$No.Fruits)

qqnorm(MergedData$No.TrmtSeeds)
qqline(MergedData$No.TrmtSeeds)


ggplot(MergedData, aes(No.TrmtSeeds)) +
  geom_histogram(binwidth = 1, position = "dodge")

ggplot(MergedData, aes(No.SeedsPerFruit)) +
  geom_histogram(binwidth = 0.5, position = "dodge")

ggplot(MergedData, aes(No.SeedsPerFlower)) +
  geom_histogram(binwidth = 0.5, position = "dodge")

ggplot(MergedData, aes(No.Fruits)) +
  geom_histogram(binwidth = 0.5, position = "dodge")
```


*Attempting an analysis similar to Niki's stigma analysis by era, even though the distribution is not normal*
```{r}
fit <- lme(No.TrmtSeeds ~ Era*Morph, random=~1|Site/Habitat, data= MergedData)
anova.lme(fit)

ggplot(MergedData, aes(x=Era, y=No.TrmtSeeds, group = Era, color = Morph)) + 
   geom_dotplot(binaxis='y', stackdir='center', binwidth = 2,
                 stackratio=1, dotsize=0.8)
```

*GLM with poisson for No.TrmtSeeds (i.e. total seeds/plant)*
```{r}
PoissonSeedsPerPlant <- glm(No.TrmtSeeds ~ Era*Morph, data = MergedData, family = poisson)
summary(PoissonSeedsPerPlant)
```

*Switching to a GLM with quasipoisson because the data is overdispersed (lambda = 33.5, not 1 in the above poisson)*
```{r}
QuasipoissonSeedsPerPlant <- glm(No.TrmtSeeds ~ Era*Morph, data = MergedData, family = quasipoisson)
summary(QuasipoissonSeedsPerPlant)
```


### I'm seeing similar results with the GLM and the LME (p-value for effect of era is ~0.0082)


*Running analyses for the rest...*
```{r}
fit <- lme(No.SeedsPerFruit ~ Era*Morph, random=~1|Site/Habitat, data= MergedData)
anova.lme(fit)

QuasipoissonSeedsPerFruit <- glm(No.SeedsPerFruit ~ Era*Morph, data = MergedData, family = quasipoisson)
summary(QuasipoissonSeedsPerFruit)

ggplot(MergedData, aes(x=Era, y=No.SeedsPerFruit, group = Era, color = Morph)) + 
  geom_dotplot(binaxis='y', stackdir='center', binwidth = 0.3,
               stackratio=1, dotsize=0.8)



## Not running this particular LME because I'm missing some values, not sure how to fix this atm
##fit <- lme(No.SeedsPerFlower ~ Era*Morph, random=~1|Site/Habitat, data= MergedData)
##anova.lme(fit)

QuasipoissonSeedsPerFlower <- glm(No.SeedsPerFlower ~ Era*Morph, data = MergedData, family = quasipoisson)
summary(QuasipoissonSeedsPerFlower)

ggplot(MergedData, aes(x=Era, y=No.SeedsPerFlower, group = Era, color = Morph)) + 
  geom_dotplot(binaxis='y', stackdir='center', binwidth = 0.3,
               stackratio=1, dotsize=0.8)
```



*The only test for which the quasipoisson glm is similar to the lme is for the first test - seeds per plant.*





